---
title: "EEDC Employee Engagement Survey"
author: "2019 Results"
output: 
  beamer_presentation:
    toc: true
params:
  response_data: NULL
  employee_data: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("plot_fns_ft.R")
source("transform_fns_ft.R")
```

# Quantitative Results

## Quantitative Questions
- 34 "quantitative" questions, categorized into 9 engagement drivers and two focus areas
  - Some questions associated with more than one driver
- New in 2019: two Pulse Check questions to measure sentiment as EEDC changes its business model
- 9 engagement drivers:
  1. Affinity: I like the place and people
  2. Communication: I get information when I need it and  am able to share my thoughts, opinions and ideas
  3. Compensation: Total rewards including pay, benefits, retirement plan, perks
  4. Development: Coaching, training and other developmental opportunities aimed at improving personal and professional career growth opportunities
  5. Empowerment: I feel supported to make decisions
  6. Performance: Execution and accomplishment of work
        
## Quantitative Questions
- 9 engagement drivers (cont.):
  7. Recognition: My efforts and accomplishments are acknowledged
  8. Relations: Relationship between the employer and employee, based on foundation of trust and respect
  9. Teamwork: Cooperative and coordinated efforts of a group working together to achieve common objectives
- Two focus areas:
  1. Change Leadership: Influence and enthuse others through personal advocacy, vision and drive, and to access resources to build a solid platform for change
  2. Direct Manager Support: Empowering others to act, foster collaboration, and build trust
    
## Analysis
- Engagement Score:
  - Percentage of responses that are **Agree** or higher
  - All questions weighted equally
- Participation Rate:
  - Percentage of respondents who answered at least one survey question
  - Employee counts are current as of the survey launch date
  - In 2017 we were less rigorous with the survey distribution list. Take 2017 participation rates with a grain of salt.

## Engagement Score Results

```{r summary, echo = FALSE}
knitr::kable(
  transform_summary_table(params$response_data),
  col.names = c("Division", "2017", "2018", "2019"),
  caption = "Engagement Score (% \'Agree\' Responses or Higher)",
  align = c('l', 'r', 'r', 'r'),
  padding = 12)
```

## Participation Results

```{r participation, echo = FALSE}
knitr::kable(
  transform_participation_table(params$response_data, params$employee_data),
  col.names = c("Division", "2017", "2018", "2019"),
  caption = "Participation Rate (Answered Past First Survey Page)",
  align = c('l', 'r', 'r', 'r'),
  padding = 12)
```

## Pulse Check Questions
- These two questions are not included in any drivers or the overall engagement score

```{r pulse_bar, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 5.5}
make_pulse_bar_plot(params$response_data, transform_pulse_bar_plot)
```

## Pulse Check Questions
- These two questions are not included in any drivers or the overall engagement score

```{r pulse_facet, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 5.5}
make_pulse_facet_plot(params$response_data, transform_pulse_facet_plot)
```

## Engagement Score by Driver and Division
```{r heatmap, echo=FALSE, message=FALSE, warning=FALSE}
make_heatmap(params$response_data, transform_yoy_plot, division, driver_all)
```

## Engagement Score by Category and Division
```{r category_heatmap, echo=FALSE, message=FALSE, warning=FALSE}
make_heatmap(params$response_data, transform_category_heatmap, division, category)
```

<!-- Year over Year Plots -->

```{r yoy_plots, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
for (d in unique(params$response_data$division)) {
  cat("\n##", " Year to Year Comparison - ", d, "  \n")
  print(make_yoy_plot(params$response_data, transform_yoy_plot, d))
  cat("  \n")
}
```

<!-- Facet Plots -->

```{r facet_plots, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
for (d in unique(params$response_data$division)) {
  cat("\n##", " Response Summary -  ", d, "  \n")
  print(make_facet_plot(params$response_data, transform_facet_plot, d, driver_all, "Driver"))
  cat("  \n")
  cat("\n##", " Response Summary -  ", d, "  \n")
  print(make_facet_plot(params$response_data, transform_category_facet_plot, d, category, "Category"))
  cat("  \n")
}
```

<!-- Detailed Heatmaps -->

```{r detail_heatmaps, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
for (d in rev(unique(params$response_data$driver_all))) {
  if (! d == "All Drivers") {
    cat("\n##", " Engagement by Question and Division",  "\n")
    print(make_detail_heatmap(params$response_data, transform_detailed_heatmap, d))
    cat("  \n")  
  }
}
```

## Year to Year Comparison - Engagement by Category

```{r category_yoy_facet, echo=FALSE, message=FALSE, warning=FALSE}
make_category_yoy_facet(params$response_data, transform_category_yoy_facet)
```

<!-- Detailed Year over Year Plots -->

```{r yoy_facets, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
for (d in rev(unique(params$response_data$driver_all))) {
  if (! d == "All Drivers") {
    cat("\n##", " Year to Year Comparison - Engagement by Question",  "\n")
    print(make_yoy_facet(params$response_data, transform_yoy_facet, d))
    cat("  \n")  
  }
}
```